---
title: "Setting up a Quantitative Project"
author: '[Your student number here]'
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: html_document
---
<!-- This is a suggested template to write the formative assignment. Feel free to make changes as appropriate according to the guidance. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
source("R/01_setup.R", local = knitr::knit_global())
```

```{r preamble, include=FALSE}
# Load packages
library(tidyverse)

# Read data
nilt <- readRDS("data/fullnilt_2012.rds")

# Subset with variables used in regression model
nilt_subset <- nilt |>
  select(persinc2, rsex, religcat, orient, uninatid, tunionsa, rsuper, rage)
```

Word count: `r wordcountaddin::word_count("Formative-template.Rmd") - 134`.
<!-- The above line will automatically calculate the word count of your report excluding the code chunks. We have manually added "- 134" to also substract from the word count the words in the info box below and the section headers. -->
<!-- Update the "- 134" in the code above to also take into account your bibliography. For example, if your bibliography is 52 characters then update the above to "- 186". -->

> **Important Information**
> 
> For this Formative Assessment you are asked to consolidate the main elements of the course across Weeks 1-5 in the form of a short report (500 words maximum). Use this template file to write your report and submit it as a knitted HTML document.
>
> The `nilt` dataset has already been loaded, variables coerced, and an `nilt_subset` dataframe created for you. Use the `nilt_subset` dataframe for this assessment. It has the same variables that will be used for the regression model in the Summative Assessment.
>
> - `persinc2` - Annual Personal Income
> - `rsex` - Sex
> - `religcat` - Religion
> - `orient` - Sexual Orientation
> - `uninatid` - NI Constitutional View
> - `tunionsa` - Trade Union Membership
> - `rsuper` - Supervisor
> - `rage` - Age
>
> For more information and guidance on the Formative Assessment, please see the [Formative Assessment page](https://ugquants.github.io/quants_workbook/assessments/formative.html) in the lab workbook.

## Introduction
<!-- Word count: approx. 200-250  -->
<!-- Provide a research question and hypothesis/hypotheses with rationale and literature to support them. -->

## Data and descriptive statistics
<!-- Word count: approx. 200-250 -->
<!-- Provide a description of the dataset and summary statistics of the model variables. -->


## Bibliography
<!-- Include bibliography here. -->
